---
title: "COVID-19 Top Counry"
author: "Patrick Kelly"
date: "2/26/2020"
output: html_document
---

### My setup

macOS Catalina 10.15.3

R version 3.6.2 (2019-12-12) -- "Dark and Stormy Night"

RStudio Version 1.1.463

[Click Here](https://www.arcgis.com/apps/opsdashboard/index.html#/bda7594740fd40299423467b48e9ecf6)"Corona Virus Data"

[Click Here](https://www.worldatlas.com/aatlas/ctycodes.htm)"Country labels"

[Click Here](https://www.worldometers.info/world-population/population-by-country/)"Country Populations"

# Corona Virus Cases per 100,000

```{r}
list.of.packages = c("tidyverse",
                     "ggplot2",
                     "countrycode",
                     "devtools",
                     "linguisticsdown",
                     "htmlwidgets")
                     new.packages <-
                     list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])]
                     if (length(new.packages))
                     install.packages(new.packages)
                     suppressMessages(library(tidyverse))
                                          suppressMessages(library(countrycode))
                     suppressMessages(library(linguisticsdown))
                     suppressMessages(library(htmlwidgets))
```

```{r}
# devtools::install_github("rensa/ggflags")
suppressMessages(library(ggflags))
```

```{r}
cases <- c(78064,1261,374,57,91,178,139)
pop <- c(1439323776,51269185,
      60461826,331002651,
      5850342,126476461,83992949)
per_100000 <- rep(1e5,6)
risk <- pop / per_100000
cases_per_100000 <- round(cases/risk,2)
cases_per_100000_2 <- as.character(cases_per_100000)
```

```{r}
dat <-
  dplyr::tibble(
  country = c(
  "China",
  "South Korea",
  "Italy",
  "USA",
  "Singapore",
  "Japan",
  "Iran"
  ),
  
  count = cases_per_100000,
  label = cases_per_100000_2,
  code = c("cn","kr","it","us","sg","jp","ir"))
p <-  dat %>% mutate(country = reorder(country, count)) %>%
  ggplot(aes(country, count, label = label)) +
  geom_bar(stat = "identity", fill = "#bd1816") +
  geom_text(nudge_y = +0.4,
  color = "black",
  size = 6) +
  geom_flag(y = -.23, aes(country = code), size = 9) +
  # scale_y_continuous(breaks = c(0, 10, 20, 30), limits = c(0, 30)) +
  labs(title = "Corona Virus Cases per 100,000 at risk by Country",
  subtitle = "February 26, 2020") +
  ggthemes::theme_economist() +
  theme(
  axis.title.y = element_blank(),
  axis.ticks.x = element_blank(),
  axis.line.x = element_blank(),
  axis.title.x = element_blank(),
  axis.text.x = element_blank()) +
  coord_flip() 
p
```

<!-- Save Plot Image -->

```{r}
# png(filename="corona_RR.png")
# plot(p)
# dev.off()

```

# Comments

When does the corona virus outbreak pgrogrss to an epidemic and then to a pandemic disease?

Maybe when a multi-continent number of cases reaches an average of 10 cases per 100,000 at risk?

Cover your mouth when sneezing and wash your hands often.

```{r, echo=FALSE}
corona <- "corona.gif"
include_graphics2(corona)
```






